Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-21 Moltres.tex

\gls{MSR} modeling efforts describe steady-state and
transient behavior. Krepel et al. extended the in-house \gls{LWR}
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. That work compared DYN3D-MSR against
experimental \gls{MSRE} data and then used it to simulate local fuel channel
blockages as well as local temperature perturbations. In a similar vein, Kophazi
et. al. used iterative coupling between in-house three-dimensional neutronic and
one-dimensional heat conduction models DALTON and THERM to analyze normal 
\gls{MSRE} operation as well as channel-blocking-incident
transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
effects of heat transfer coefficients as well as thermal
coupling between fuel channels through moderator heat conduction. More recently,
Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
\gls{MSBR} using the commercial finite element package COMSOL
Multiphysics \cite{cammi_multi-physics_2011}. That work directly solved the 
fuel salt velocity field, used heterogeneous group constants
in fuel and moderator regions, and employed a software package (COMSOL)
intrinsically designed for coupled multi-physics simulation.
Additionally, Aufiero et. al \cite{aufiero_development_2014} have begun to 
approach transient simulations in the \gls{MSFR} by directly coupling Serpent 2 
Monte Carlo neutronics with OpenFOAM \cite{weller_tensorial_1998} thermal-hydraulics.

The present work introduces the open source simulation tool, Moltres
\cite{lindsay_moltres_2017}, for simulating \glspl{MSR}.  By implementing
deterministic neutronics and thermal hydraulics in the context of the
\gls{MOOSE} finite element modeling framework, Moltres solves arbitrary-group
neutron diffusion, temperature, and precursor governing equations in anywhere
from one to three dimensions and can be deployed on an arbitrary number of
processing units. Through its computing power, Moltres is devoted to previously
unmatched fidelity in coupled neutronics and thermal hydraulics \gls{MSR}
simulation.

>>>>

Simulation tools developed by many authors successfully describe steady-state and
transient behavior of myriad \gls{MSR} concepts. Krepel et al. extended the in-house \gls{LWR}
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. That work compared DYN3D-MSR against
experimental \gls{MSRE} data and then used it to simulate local fuel channel
blockages as well as local temperature perturbations.

In a similar vein, Kophazi et al. used iterative coupling between in-house
three-dimensional neutronic and one-dimensional heat conduction models DALTON
and THERM to analyze normal \gls{MSRE} operation as well as
channel-blocking-incident transients \cite{kophazi_development_2009}. The
Kophazi model added entrance effects of heat transfer coefficients as well as
thermal coupling between fuel channels through moderator heat conduction. More
recently, Cammi et al. performed a 2D-axisymmetric single-channel analysis of
the \gls{MSBR} using the commercial finite element package COMSOL Multiphysics
\cite{cammi_multi-physics_2011}. That work directly solved the fuel salt
velocity field, used heterogeneous group constants in fuel and moderator
regions, and employed the \gls{COMSOL} software package intrinsically designed
for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
colleagues conducted a benchmarking exercise \cite{fiorina_modelling_2013} in
which this Politecnico di Milano approach was expanded to a multi-channel model 
of the \gls{MSFR} and compared to code from the University of Delft
\cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach in
\cite{kophazi_development_2009}. These models showed good agreement for
multiple accident transients. Meanwhile, leveraging lessons learned from these 
efforts has resulted in a multiscale approach from Zanetti et al. 
\cite{zanetti_geometric_2015} successfully combines high and low geometric 
fidelity for graphite-moderated \glspl{MSR}.

More recently, Aufiero et al. \cite{aufiero_development_2014} have begun to
approach transient simulations in the \gls{MSFR} within the finite volume
OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
benefits from pre-implemented turbulence models available in the OpenFOAM
library and captures the full-core three-dimensional geometry of the reactor
primary circuit.  OpenFOAM \gls{CFD} has additionally been shown by Laureau et
al. \cite{laureau_transient_2017} to couple well with Transient Fission Matrix
neutronics within the \gls{MSFR}.

The present work introduces the open source simulation tool, Moltres
\cite{lindsay_moltres_2017}, for simulating \glspl{MSR}.  By implementing
deterministic neutronics and thermal hydraulics in the context of the
\gls{MOOSE} finite element modeling framework, Moltres solves arbitrary-group
neutron diffusion, temperature, and precursor governing equations in anywhere
from one to three dimensions and can be deployed on an arbitrary number of
processing units.
